Exposing Disputed Statements on the Web

### 2009-03-23 papers/uist_thinklink/thinklink.tex
Spell check

%\documentclass{article}
\documentclass{chi2009}
\usepackage{times}
%\usepackage{uist}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
% \usepackage[pdftex]{hyperref}
% \hypersetup{%
% pdftitle={Browsing the Web of Factual Claims},
% pdfauthor={Beth Trushkowsky and Rob Ennals},
% pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
% bookmarksnumbered,
% pdfstartview={FitH},
% colorlinks,
% citecolor=black,
% filecolor=black,
% linkcolor=black,
% urlcolor=black,
% breaklinks=true,
% }

@@

\author{
\parbox[t]{9cm}{\centering
	     {\em Author Name removed for blind review}\\
}
\parbox[t]{9cm}{\centering
	     {\em Author Name removed for blind review}}
}

@@

\abstract
We present Think Link, a browser extension that aims to let users see when the information they are reading presents only one side of a disputed issue. As the user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on such a disputed claim then Think Link will show tem an argument graph showing the best evidence for and against the claim being true, as determined by other users of Think Link.

@@

The web provides users with a huge number of pages that they can read, but extracting accurate and balanced information from these pages can be difficult. Not everything on the web is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and many web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}. If a user is to form a rounded opinion about a topic then they will need to either stick to sources that they trust or spend time looking for evidence on other web sites that supports or opposes what they read. Even if a user tries hard to research every topic they read, they can still get caught out by beliefs that they had not realised were disputed.

@@

Think Link is designed to cator to two distinct groups of people. Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them. Sceptical readers install Think Link as a browser plugin so that they can see when things they read and disputed and find other links that present other points of view. A reader may of course be an activist for one issue and a sceptical reader for others.

The design of Think Link was guided by two user studies, in which we observed the behaviour of users who fitted the roles of Activist or Sceptical Reader.

\todo{Talk about automatically including all arguments from snopes}.

@@

Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}. IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue. Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.

@@

When chosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use. For Think Link, we have tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model. The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.

@@

If a sceptical reader has installed the Think Link browser extension then Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is. If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evedience for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).

Since the purpose of a highlight is to alert the user to claims that they had not realised were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious. A user can click the ``don't highlight this claim again'' button to tell Think Link that they are aware of the contentious nature of this claim and do not wish to be alerted about it again.

@@

In our user studies, we found that users wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a panel describes a disputed claim, then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right. To emphasise the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

@@

The panel for a claim lists evidence that will help a user decide whether the claim is true. Evidence is categorised as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support the truth of this claim.

@@

The page annotation script is a javascript file that can be included into any HTML page. When it is run on a page it sends the page URL to the server, asking it to send back information about any contentious snippets on that page. If any such snippets are found, the page modification script highlights them in red. If the user clicks on a highlighted snippet then it shows an iframe containing a visualisation from whatever visualization server it has been configured to use.

@@

\subsubsection{Choosing what to mark as a snipet}

@@

Several users wanted to mark up a table or an image as a snippet. This is valid behaviour -- a table or image is often useful evidence for a claim; however it is not currently supported by Think Link. In future versions of Think Link we intend to support this behaviour.

@@

Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. Similarly, many users expressed a desire to mark claims as being ``related'' without supporting or opposing each other. For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''. In the first prototypes, a user needed to chose between ``supports/opposes'' when connecting two claims together (follwing gIBIS~\cite{Conklin1987a}). In the final interface we introduced a ``related-to'' link type to allow users to connect claims that they thought should be related but which didn't confirm to a simple pro/con relationship.

@@

The first two versions of Think Link used a drag-and-drop interface to allow a user to create links between claims. In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree. In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphore, providing two identical browser windows that a user could drag and drop claims between. In both cases, we found that users would often not intially realise they could use drag and drop to arganize claims, even when we added a prominant information message at the top of the display (Figure~\ref{secondbrowser}). We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections. In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.

@@

Acknowledgements ommitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.

>>>>

%\documentclass{article}
\documentclass{chi2009}
\usepackage{times}
%\usepackage{uist}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}

@@

\author{
\parbox[t]{9cm}{\centering
	     {\em Author names removed for blind review}\\
}
}

@@

\abstract
We present Think Link, a browser extension that aims to let users see when the information they are reading presents only one side of a disputed issue. As the user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on such a disputed claim then Think Link will show them an argument graph showing the best evidence for and against the claim being true, as determined by other users of Think Link.

@@

The web provides users with a huge number of pages that they can read, but extracting accurate and balanced information from these pages can be difficult. Not everything on the web is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and many web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}. If a user is to form a rounded opinion about a topic then they will need to either stick to sources that they trust or spend time looking for evidence on other web sites that supports or opposes what they read. Even if a user tries hard to research every topic they read, they can still get caught out by beliefs that they had not realized were disputed.

@@

Think Link is designed to cater to two distinct groups of people. Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them. Sceptical readers install Think Link as a browser plugin so that they can see when things they read and disputed and find other links that present other points of view. A reader may of course be an activist for one issue and a sceptical reader for others.

The design of Think Link was guided by two user studies, in which we observed the behavior of users who fitted the roles of Activist or Sceptical Reader.

\todo{Talk about automatically including all arguments from Snopes}.

@@

Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}. IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue. Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2006} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.

@@

When choosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use. For Think Link, we have tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model. The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.

@@

If a sceptical reader has installed the Think Link browser extension then Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is. If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).

Since the purpose of a highlight is to alert the user to claims that they had not realized were contentious, there is little benefit in highlighting snippets that make claims that the user already realizes are contentious. A user can click the ``don't highlight this claim again'' button to tell Think Link that they are aware of the contentious nature of this claim and do not wish to be alerted about it again.

@@

In our user studies, we found that users wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a panel describes a disputed claim, then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right. To emphasis the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

@@

The panel for a claim lists evidence that will help a user decide whether the claim is true. Evidence is categorized as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support the truth of this claim.

@@

The page annotation script is a javascript file that can be included into any HTML page. When it is run on a page it sends the page URL to the server, asking it to send back information about any contentious snippets on that page. If any such snippets are found, the page modification script highlights them in red. If the user clicks on a highlighted snippet then it shows an iframe containing a visualization from whatever visualization server it has been configured to use.

@@

\subsubsection{Choosing what to mark as a snippet}

@@

Several users wanted to mark up a table or an image as a snippet. This is valid behavior -- a table or image is often useful evidence for a claim; however it is not currently supported by Think Link. In future versions of Think Link we intend to support this behavior.

@@

Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. Similarly, many users expressed a desire to mark claims as being ``related'' without supporting or opposing each other. For example ``America did not sign the Kyoto Protocol'' {\it is related to} ``America was right to not sign the Kyoto Protocol''. In the first prototypes, a user needed to chose between ``supports/opposes'' when connecting two claims together (following gIBIS~\cite{Conklin1987a}). In the final interface we introduced a ``related-to'' link type to allow users to connect claims that they thought should be related but which didn't confirm to a simple pro/con relationship.

@@

The first two versions of Think Link used a drag-and-drop interface to allow a user to create links between claims. In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree. In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between. In both cases, we found that users would often not intially realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}). We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections. In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.

@@

Acknowledgements omitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.
